---
title: "Plotly Package Review"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package Overview

## History of Plotly 
Plotly was founded by Alex Johnson, Jack Parmer, Chris Parmer, and Matthew Sundquist.  Their background lies in energy and data analysis.  While working for the data science program of a California-based cleantech company, Alex, Jack, Chris, and Matthew found themselves facing the seemingly simple problem of finding a way to meaningfully and easily share the data they've gathered. Even after collecting, analyzing, and sorting the data, they felt that there were still important questions that had to be answered: 

How do we share what we've learned with others in a meaningful way? 
## Usage of Plotly 
Plotly is a graphing library that makes interactive, publication-quality graphs. It is an open-source package that can be found on numerous platforms including R, Python, .NET, JS, and Julia.  It can make visualizations ranging from basic bar-graphs to maps, 3d charts, and animated charts.  

##Version History

##Dependencies

##Usage

##Examples of Usage

```{r}

```

